Deployable Probabilistic Programming

### 2019-04-17 paper/paper.tex
more references, plan for related work
better rendering of listings

\lstset{ % add your own preferences
    frame=single,
    basicstyle=\ttfamily\footnotesize,
    numbers=none,
    numbersep=4pt,
	framexleftmargin=10pt,
    showstringspaces=false,
    tabsize=4,
    language=Golang % this is it !
}

@@

\section{Related Work}

Integrated probabilistic programming (Figaro, Anglican, Turing).

@@

\begin{figure*}
	\begin{minipage}{0.45\textwidth}
\begin{lstlisting}[language=Stan,numbers=left]
data {
  int<lower=0> J;
  vector[J] y;
  vector<lower=0>[J] sigma;
}

@@

\centering
a. Stan
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\textwidth}
\begin{lstlisting}[numbers=left]
type Model struct {
  J          int
  Y          []float64
  Sigma      []float64
}

@@

\begin{figure}
\begin{lstlisting}[numbers=left]
type Model struct {
  Data  [][]float64
}

@@

\begin{figure}
\begin{lstlisting}[numbers=left]
type Model struct {
  Data  []float64 // samples
  NComp int       // number of components
}

@@

  // Compute log likelihood of mixture
  // given the data
  for i := 0; i != len(m.Data); i++ {
    var l float64
    for j := 0; j != m.NComp; j++ {
      lj := Normal.Logp(mu[j], sigma[j], m.Data[i])
      if j == 0 {
        l = lj
      } else {
        l = mathx.LogSumExp(l, lj)
      }
    }
    ll += l
  }
  return ll
}
\end{lstlisting}
\caption{Gaussian mixture: Infergo can handle models with
	dynamic control structure.}
\label{fig:linear-regression}
\end{figure}

>>>>

\lstset{ % add your own preferences
    frame=single,
    basicstyle=\ttfamily\footnotesize,
    numbers=none,
    numbersep=4pt,
    showstringspaces=false,
    tabsize=4,
    language=Golang % this is it !
}

@@

\section{Related Work}
Probabilistic programming languages \cite{GS15}, \cite{MPY+18},
\cite{Stan17}, \cite{GGS19}.

Integrated probabilistic programming (Figaro~\cite{P09},
Anglican~\cite{TMY+16}, Turing~\cite{GXG18}).

@@

\begin{figure*}
	\begin{minipage}{0.45\textwidth}
	\begin{lstlisting}[language=Stan,framexleftmargin=10pt,numbers=left]
data {
  int<lower=0> J;
  vector[J] y;
  vector<lower=0>[J] sigma;
}

@@

\centering
a. Stan
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\textwidth}
\begin{lstlisting}[framexleftmargin=10pt,numbers=left]
type Model struct {
  J          int
  Y          []float64
  Sigma      []float64
}

@@

\begin{figure}
\begin{lstlisting}[framexleftmargin=10pt,numbers=left]
type Model struct {
  Data  [][]float64
}

@@

\begin{figure}
\begin{lstlisting}[framexleftmargin=10pt,numbers=left]
type Model struct {
  Data  []float64 // samples
  NComp int       // number of components
}

@@

  // Compute log likelihood of mixture
  // given the data
  for i := 0; i != len(m.Data); i++ {
    var l float64
    for j := 0; j != m.NComp; j++ {
      lj := Normal.Logp(mu[j], sigma[j], m.Data[i])
      if j == 0 {
        l = lj
      } else {
        l = mathx.LogSumExp(l, lj)
      }
    }
    ll += l
  }
  return ll
}
\end{lstlisting}
\caption{Gaussian mixture: Infergo can handle models with
	dynamic control structure.}
\label{fig:gaussian-mixture}
\end{figure}
